Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-12-27 paper/lncsFormat.tex
remove citation of framenet

The second group methods detect events by \textit{leveraging extra information}. 
\cite{huang2016efficient} incorporates user's and the followees' profiles to help to detect the events of public concern. 
However it's not easy to get this kind contextual information.
\cite{osborne2012bieber} compares two time series generated by event-related tweets and the corresponding Wikipedia article's page views, and further filter out spurious events of microblogs.
Twevent \cite{Twevent2012} divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia, then detect the bursty segments and cluster these segments into candidate events for necessary post processings.
But as shown in \cite{Yan:2015wm}, Twevent is still hampered by the performance of simply clustering the bursty segments.
Beyond the scope of microblog stream, \cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
And \cite{liuleveraging2016} leverages the ACE corpus\cite{doddington2004automatic} and the structure of FrameNet\cite{baker1998berkeley} to improve the event detection within FrameNet, but has not shown how to apply the knowledge base for more general unstructured corpus.
In a nutshell, existing works are different from ours, as we transfer the category information of knowledge base into microblog's words and get the finer processing objects in event detection, rather than treating the knowledge base as a lookup table or a comparison base.

@@

\subsection{Extracting Category-Level Topics in Knowledge Base}\label{subsec:hs_initialization}
In this part, we discuss in detail how to extract the \textit{category-level topics in knowledge base} on the given categories. 
The knowledge base such as Wikipedia has the structure of classes, subclasses, instances, and the edges between them. 
This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
But the reasoning and maintenance of knowledge on the graph is usually expensive\cite{bursztyn2015reasoning}. 
To make a trade-off between cost and performance, we use the lightweight data structure \textit{topics} to represent the knowledge at category(class) level.
And the knowledge base's threefold structure \(G^{(0)}\), \(G^{(1)}\), \(G^{(2)}\) benefits the extraction of \textit{category-level topics}.

@@

\textbf{Benchmarks and Evaluation Metrics.} 
The evaluation is conducted on two benchmarks.
The first benchmark on \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}, which all exist in our rebuilt dataset on the \textit{Edinburgh twitter}'s IDs.
These labeled events focus on the events that are both mentioned in twitter and newswire,e.g. \textit{``Oslo Attacks"} and \textit{``US Increasing Debt Ceiling"}, but still miss many important events such as \textit{``Hurricane Irene"}, \textit{``Al-Qaida's No. 2 Leader Being Killed"}, and popular events such as \textit{``Harry Potter and the Deathly Hallows (Part 2)"}.
To include these important events and enlarge the ground truth of realistic events pool, we build the second benchmark carefully.
We manually evaluate the candidate events detected by LSH,  \textsc{TransDetector}, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, with the help of the Wikipedia Current Event Portal\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} and a local search engine built on Lucene.
The labeling process generates the Benchmark2, and contains 395 events.
We use precision and recall to evaluate each method on both benchmarks, and utilize the DERate(Duplicate Event Rate) metric\cite{Twevent2012} to measure the readability of detected events.
The smaller the metric DERate, the less duplicate events to be filtered out in the application.

@@

>>>>

The second group methods detect events by \textit{leveraging extra information}. 
\cite{huang2016efficient} incorporates user's and the followees' profiles to help to detect the events of public concern. 
However it's not easy to get this kind contextual information.
\cite{osborne2012bieber} compares two time series generated by event-related tweets and the corresponding Wikipedia article's page views, and further filter out spurious events of microblogs.
Twevent \cite{Twevent2012} divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia, then detect the bursty segments and cluster these segments into candidate events for necessary post processings.
But as shown in \cite{Yan:2015wm}, Twevent is still hampered by the performance of simply clustering the bursty segments.
Beyond the scope of microblog stream, \cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
%And \cite{liuleveraging2016} leverages the ACE corpus\cite{doddington2004automatic} and the structure of FrameNet\cite{baker1998berkeley} to improve the event detection within FrameNet, but has not shown how to apply the knowledge base for more general unstructured corpus.
In a nutshell, existing works are different from ours, as we transfer the category information of knowledge base into microblog's words and get the finer processing objects in event detection, rather than treating the knowledge base as a lookup table or a comparison base.

@@

\subsection{Extracting Category-Level Topics in Knowledge Base}\label{subsec:hs_initialization}
In this part, we discuss in detail how to extract the \textit{category-level topics in knowledge base} on the given categories. 
The knowledge base such as Wikipedia has the structure of classes, subclasses, instances, and the edges between them. 
This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
But the the query on the large graph is usually very expensive\cite{huang2011scalable}. 
To make a trade-off between cost and performance, we use the lightweight data structure \textit{topics} to represent the knowledge at category(class) level.
And the knowledge base's threefold structure \(G^{(0)}\), \(G^{(1)}\), \(G^{(2)}\) benefits the extraction of \textit{category-level topics}.

@@

\textbf{Benchmarks and Evaluation Metrics.} 
The evaluation is conducted on two benchmarks.
The first benchmark on \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}, which all exist in our rebuilt dataset on the \textit{Edinburgh twitter}'s IDs.
These labeled events focus on the events that are both mentioned in twitter and newswire,e.g. \textit{``Oslo Attacks"} and \textit{``US Increasing Debt Ceiling"}, but still miss many important events such as \textit{``Hurricane Irene"}, \textit{``Al-Qaida's No. 2 Leader Being Killed"}, and popular events such as \textit{``Harry Potter and the Deathly Hallows (Part 2)"}.
To include these important events and enlarge the ground truth of realistic events pool, we build the second benchmark carefully.
We manually evaluate the candidate events detected by LSH,  \textsc{TransDetector}, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, with the help of the \textit{Wikipedia Current Event Portal}\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} and a local search engine built on Lucene.
The labeling process generates the Benchmark2, and contains 395 events.
We use precision and recall to evaluate each method on both benchmarks, and utilize the DERate(Duplicate Event Rate) metric\cite{Twevent2012} to measure the readability of detected events.
The smaller the metric DERate, the less duplicate events to be filtered out in the application.

@@

\section*{Acknowledgments}\label{sec:Acknowledgments}
This research is supported by the Natural Science Foundation of China (Grant No. 61300003, 61572043), and the Specialized Research Fund for the Doctoral Program of Higher Education (Grant No. 20130001120001).
